Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Quick review to Eval section

\subsection{Policy Durability}

@@

\section{Evaluation}\label{evaluation}
We have conducted our evaluation on CloudLab as well as our own 20 node cluster. We follow the ``Popper Convention"~\cite{} so as to try and make our experiments as reproducible as possible. We have a GitHub repository with our source code,  experimental environment, configuration parameters, and workloads in a GitHub repository. Due to the double-blind policy, we have temporarily disabled the links to our graphs and experimental details.

@@

While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centeralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

@@

The real cost of interface management, in addition to cluster-wide propagation
of interface updates, includes the network round-trip to the interface
management service, the PAXOS commit protocol, and other factors such as system
load. By default PAXOS proposals occur periodically with a 1 second interval in
order to accumulate updates. In a minimum, realistic quorum of 3 monitors using
HDD-based storage, we were able to decrease this interval to an average of 222
ms.

\subsection{MDS as a Sequencer}

@@

\textbf{The Malacology Principle:} Re-uses the Ceph metadata migration, load
balancing, cache coherence, and capabilities subsystems of the MDS. Applying
Mantle's load balancing policy shows 2.02\(\times\) performance improvement and
16\% degradation in performance over the baseline, even though the baseline has
half as many clients.

@@

\textbf{The Malacology Principle:} Re-uses the Ceph metadata protocols for
failure detection and recovery. The sequencer recovers in 15 seconds on a new
MDS and it maintains the same throughput that it had before the failure.

>>>>

\subsection{Making Policies Durable}

@@

\section{Evaluation}\label{evaluation}
We have conducted our evaluation on CloudLab as well as our own 20 node cluster. We follow the ``Popper Convention"~\cite{anonymous} so as to try and make our experiments as reproducible as possible. We have a GitHub repository with our source code,  experimental environment, configuration parameters, and workloads in a GitHub repository. Due to the double-blind policy, we have temporarily disabled the links to our graphs and experimental details.

@@

\textbf{The Malacology Approach:} Re-use the capability management features of the MDS.
While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centeralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

@@

\textbf{The Malacology Approach:} Re-use Ceph's Monitor functionality to 
propagate application-specific state that needs to be highly-available and 
strongly consistent.
The real cost of interface management, in addition to cluster-wide propagation
of interface updates, includes the network round-trip to the interface
management service, the PAXOS commit protocol, and other factors such as system
load. By default PAXOS proposals occur periodically with a 1 second interval in
order to accumulate updates. In a minimum, realistic quorum of 3 monitors using
HDD-based storage, we were able to decrease this interval to an average of 222
ms.

\subsection{MDS as a ZLog Sequencer}

@@

\textbf{The Malacology Approach:} Re-use the Ceph metadata migration, load
balancing, cache coherence, and capabilities subsystems of the MDS. Applying
Mantle's load balancing policy shows 2.02\(\times\) performance improvement and
16\% degradation in performance over the baseline, even though the baseline has
half as many clients.

@@

\textbf{The Malacology Approach:} Re-use the Ceph metadata protocols for
failure detection and recovery. The sequencer recovers in 15 seconds on a new
MDS and it maintains the same throughput that it had before the failure.
